$\ast$$\ast$$\ast$\-W\-O\-R\-K I\-N P\-R\-O\-G\-R\-E\-S\-S$\ast$$\ast$$\ast$ 

 \subsection*{$\vert$ I\-N\-F\-O\-R\-M\-A\-T\-I\-O\-N A\-B\-O\-U\-T O\-U\-R P\-P\-A A\-N\-D C\-O\-N\-T\-R\-I\-B\-U\-T\-I\-N\-G T\-O T\-H\-E T\-S\-G\-L D\-E\-B\-I\-A\-N P\-A\-C\-K\-A\-G\-E (Last updated\-: 08/09/16) $\vert$ }

As of summer 2016, we currently have a P\-P\-A (Personal Package Archive) on \href{https://launchpad.net/}{\tt Launchpad} for our T\-S\-G\-L Debian packages.

You can visit our P\-P\-A by clicking \href{https://launchpad.net/~tsgl-test/+archive/ubuntu/tsgl-dev}{\tt here}.

We also have a moderated team which allows us to add users, like you, so that the Debian package can be updated by others.

You will, however, need a Launchpad account in order to be added to our team. 

 \subsection*{$\vert$ Launchpad account $\vert$ }

$\ast$$\ast$$\ast$\-N\-O\-T\-E\-:$\ast$$\ast$$\ast$ If you have already created a Launchpad account, feel free to skip this section.

Follow the process as described \href{https://login.launchpad.net/+new_account}{\tt here} in order to create an account.

Once you create your account (and have validated your email), log into \href{https://launchpad.net/}{\tt Launchpad}. 

 \subsection*{$\vert$ Signing the Ubuntu Code of Conduct $\vert$ }

$\ast$$\ast$$\ast$\-N\-O\-T\-E\-:$\ast$$\ast$$\ast$ If you have already signed the Ubuntu Code of Conduct, feel free to skip this section.

Now, go to your profile (click on your username; it should be next to the {\ttfamily Log Out} button on the right corner of the webpage).

On your profile page, you should see {\ttfamily Signed Ubuntu Code of Conduct\-:} somewhere. If you have created a new account, it should say {\ttfamily No}.

In order to sign packages, upload them to P\-P\-As, create your own P\-P\-As, etcetera you'll have to sign that Code of Conduct.

\href{https://launchpad.net/codeofconduct}{\tt Follow this process in order to sign the Ubuntu Code of Conduct}.

$\ast$$\ast$$\ast$\-N\-O\-T\-E\-:$\ast$$\ast$$\ast$ See \mbox{[}\mbox{[}G\-P\-G keys and You\mbox{]}\mbox{]} on how to create a G\-P\-G key and get its fingerprint for step 1. 

 \subsection*{$\vert$ Contributing to the T\-S\-G\-L Debian package $\vert$ }