$\ast$$\ast$$\ast$\-N\-O\-T\-E\-:$\ast$$\ast$$\ast$ This process is for people who have cloned the repository on Linux/\-Mac. Windows users may use \href{https://git-scm.com/download/win}{\tt Git Bash}, though that has not been tested.

$\ast$$\ast$$\ast$\-N\-O\-T\-E\-:$\ast$$\ast$$\ast$ Before updating the Doxygen, please see the \href{https://github.com/Calvin-CS/TSGL/blob/master/READMEMISC.txt}{\tt R\-E\-A\-D\-M\-E\-M\-I\-S\-C.\-txt} file. {\bfseries You will not be able to update the Doxygen correctly if you fail to read \href{https://github.com/Calvin-CS/TSGL/blob/master/READMEMISC.txt}{\tt R\-E\-A\-D\-M\-E\-M\-I\-S\-C.\-txt} first!}

$\ast$$\ast$$\ast$\-B\-I\-G N\-O\-T\-E\-:$\ast$$\ast$$\ast$ You $\ast$$\ast$$\ast$\-N\-E\-E\-D$\ast$$\ast$$\ast$ doxygen 1.\-8.\-6 in order to update the documentation correctly. Previous versions will cause a $\ast$$\ast$$\ast$\-L\-O\-T$\ast$$\ast$$\ast$ of problems.

In order to provide an A\-P\-I and extensive documentation for the T\-S\-G\-L library, we rely on a tool known as \href{http://www.stack.nl/~dimitri/doxygen/}{\tt Doxygen}.

We also use the \href{https://github.com/Calvin-CS/TSGL/wiki}{\tt Wiki} pages to provide important information about the T\-S\-G\-L library (Debian and R\-P\-M packages, F\-A\-Qs, etc...).

If you take a look at our \href{http://calvin-cs.github.io/TSGL/html/pages.html}{\tt Doxygen} pages, you'll notice that our Wiki pages also show up as well as the documentation for the T\-S\-G\-L code.

Which means, in order to keep these two up-\/to-\/date, whenever you make a change to the Wiki pages, you'll have to also update the Doxygen pages.

If you only added new documentation to the T\-S\-G\-L source code, then you do $\ast$$\ast$$\ast$\-N\-O\-T$\ast$$\ast$$\ast$ have to update the Wiki pages.

We provide two different processes for each situation. Follow the one that matches closely to your situation.

\subsection*{Updating the Doxygen pages only}

1). Navigate into the T\-S\-G\-L root directory (where the Makefile is).

2). Type \char`\"{}make cleandocs\char`\"{}.

3). cd into the docs/ directory.

4). Type \char`\"{}rm -\/r html\char`\"{}.

5). cd back out of the docs/ directory (cd ../).

6). Type \char`\"{}make docs\char`\"{}.

7). cd into the docs/ directory again.

8). Type \char`\"{}git add -\/-\/all\char`\"{} .

9). Do a \char`\"{}git commit -\/m \char`\"{}\char`\"{} \char`\"{} inside of the docs/ directory.

10). Type \char`\"{}git push origin gh-\/pages\char`\"{} . This should push the new Doxygen pages to our gh-\/pages branch (where our documentation $\ast$$\ast$$\ast$\-S\-H\-O\-U\-L\-D$\ast$$\ast$$\ast$ reside).

11). cd back out of the docs/ directory (cd ../).

12). Type \char`\"{}git add .\char`\"{} .

13). Do a \char`\"{}git commit -\/m \char`\"{}\char`\"{} \char`\"{}.

14). Type \char`\"{}git push origin master\char`\"{}. This should update the docs/ submodule inside of our main Git\-Hub branch.

\subsection*{Updating the Wiki and Doxygen pages}

1). Make any changes to the Wiki pages and save them.

2). Navigate into the T\-S\-G\-L root directory (where the Makefile is).

3). Type \char`\"{}git submodule update -\/-\/remote\char`\"{}. This should cause the docs-\/wiki/ submodule to update (and docs/ if it has been updated recently).

4). Type \char`\"{}git add .\char`\"{} . This should add the docs-\/wiki/ submodule (and possibly the docs/ submodule if it has been updated recently).

5). Do a \char`\"{}git commit -\/m \char`\"{}\char`\"{} \char`\"{}.

6). Type \char`\"{}git push origin master\char`\"{} . This should push the changes to the main Git\-Hub branch.

7). Type \char`\"{}make cleandocs\char`\"{}.

8). cd into the docs/ directory.

9). Type \char`\"{}rm -\/r html\char`\"{}.

10). cd back out of the docs/ directory (cd ../).

11). Type \char`\"{}make docs\char`\"{}.

12). cd into the docs/ directory again.

13). Type \char`\"{}git add -\/-\/all\char`\"{} .

14). Do a \char`\"{}git commit -\/m \char`\"{}\char`\"{} \char`\"{} inside of the docs/ directory.

15). Type \char`\"{}git push origin gh-\/pages\char`\"{} . This should push the new Doxygen pages to our gh-\/pages branch (where our documentation $\ast$$\ast$$\ast$\-S\-H\-O\-U\-L\-D$\ast$$\ast$$\ast$ reside).

16). cd back out of the docs/ directory (cd ../).

17). Type \char`\"{}git add .\char`\"{} .

18). Do a \char`\"{}git commit -\/m \char`\"{}\char`\"{} \char`\"{}.

19). Type \char`\"{}git push origin master\char`\"{}. This should update the docs/ submodule inside of our main Git\-Hub branch. 