$\ast$$\ast$$\ast$\-N\-O\-T\-E\-:$\ast$$\ast$$\ast$ This process is for people who have cloned the repository on Linux/\-Mac. Windows users may use \href{https://git-scm.com/download/win}{\tt Git Bash}, though that has not been tested.

$\ast$$\ast$$\ast$\-N\-O\-T\-E\-:$\ast$$\ast$$\ast$ Before updating the Doxygen, please see the \href{https://github.com/Calvin-CS/TSGL/blob/master/READMEMISC.txt}{\tt R\-E\-A\-D\-M\-E\-M\-I\-S\-C.\-txt} file. {\bfseries You will not be able to update the Doxygen correctly if you fail to read \href{https://github.com/Calvin-CS/TSGL/blob/master/READMEMISC.txt}{\tt R\-E\-A\-D\-M\-E\-M\-I\-S\-C.\-txt} first!}

$\ast$$\ast$$\ast$\-B\-I\-G N\-O\-T\-E\-:$\ast$$\ast$$\ast$ You $\ast$$\ast$$\ast$\-N\-E\-E\-D$\ast$$\ast$$\ast$ doxygen 1.\-8.\-6 in order to update the documentation correctly. Previous versions will cause a $\ast$$\ast$$\ast$\-L\-O\-T$\ast$$\ast$$\ast$ of problems.

In order to provide an A\-P\-I and extensive documentation for the T\-S\-G\-L library, we rely on a tool known as \href{http://www.stack.nl/~dimitri/doxygen/}{\tt Doxygen}.

If you need to update our Doxygen pages for whatever reason (you've added a new class, found a typo and fixed it, etc...), follow this process (via terminal or command-\/line)\-:

1). Navigate into the T\-S\-G\-L root directory (where the Makefile is).

2). Type \char`\"{}make cleandocs\char`\"{}.

3). cd into the \char`\"{}docs\char`\"{} folder.

4). Type \char`\"{}git rm -\/r html\char`\"{}.

5). cd back out of the \char`\"{}docs\char`\"{} folder (cd ..).

6). Type \char`\"{}make docs\char`\"{}.

7). cd into the \char`\"{}docs\char`\"{} folder again.

8). Type \char`\"{}git add html\char`\"{}.

9). Do a \char`\"{}git commit\char`\"{} inside of the docs folder.

10). Type \char`\"{}git push origin gh-\/pages\char`\"{}.

11). cd back out of the \char`\"{}docs\char`\"{} folder.

12). Do a \char`\"{}git add docs\char`\"{}.

13). Do a \char`\"{}git commit\char`\"{}.

14). Type \char`\"{}git push origin master\char`\"{}. 